r5r: Rapid Realistic Routing with R5 in R

### 2020-09-17 r-package/paper2020/paper2020.Rmd
updates paper's travel time matrix example

```{r, message = FALSE}
# calculate a travel time matrix
ttm <- travel_time_matrix( r5r_core = r5r_core,
                           origins = points,
                           destinations = points,
                           trip_date = "2019-05-20",
                           departure_time = "14:00:00",
                           mode = c("WALK", "TRANSIT"),
                           max_street_time = 7200,
                           max_trip_duration = 7200
                          )
head(ttm)
```

>>>>

```{r, message = FALSE}
mode <- c("WALK", "TRANSIT")
max_walk_dist <- Inf
max_trip_duration <- 120L
departure_datetime <- as.POSIXct("13-03-2019 14:00:00",
                                 format = "%d-%m-%Y %H:%M:%S",
                                 tz = "America/Sao_Paulo")

# estimate travel time matrix
ttm <- travel_time_matrix(r5r_core,
                          origins = points,
                          destinations = points,
                          mode,
                          departure_datetime,
                          max_walk_dist,
                          max_trip_duration)

head(ttm)
```
